### 2017-11-10 paper/sections/4_dynamic-policies.tex
paper: addresses #9
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: addresses #11
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Using the Mantle policy engine, we test a variety of cache management tools and
algorithms on a single in-memory database node using the keyspace analysis in
Section~\S\ref{sec:parsplice-keyspace-analysis}. These strategies are
implemented as the ``when" and ``how much" policies from the Mantle API; the
``where" callback does not make sense for a single node (segments are either in
the cache or they are not). The evaluation metric is the accuracy and runtime
of each strategy; the strategy should be accurate enough so as to sacrifice
negligible performance and fast enough to run as often as we want to detect
regimes.

@@

The results for different cache sizes for a growth rate of \(\Delta_1\) over a
2.5 hour run across 256 workers is shown in
Figure~\ref{fig:methodology-tradeoff}.  ``Baseline" is the performance of
unmodified ParSplice  measured in trajectory duration (\(y\) axis) and
utilization is measured with memory footprint of just the cache (\(y2\) axis).
The other graph shares the \(y\) axis and shows the trade-off of constraining
the cache to different sizes.  The error bars are the standard deviation of 3
runs.

@@

>>>>

Using the Mantle policy engine, we test a variety of cache management tools and
algorithms on a single in-memory database node using the keyspace analysis in
Section~\S\ref{sec:parsplice-keyspace-analysis}. These strategies are
implemented as the ``when" and ``how much" policies from the Mantle API; the
``where" callback does not make sense for a single node (segments are either in
the cache or they are not). The evaluation metric is the accuracy and runtime
of each strategy; the strategy should be accurate enough so as to sacrifice
negligible performance and fast enough to run as often as we want to detect
regimes. The goal of the following sections is not to find an optimal solution,
as this can be done with parameter sweeps for thresholds; rather, we try to
find techniques that work for a range of inputs and system setups.

@@

The results for different cache sizes for a growth rate of \(\Delta_1\) over a
2.5 hour run across 256 workers is shown in
Figure~\ref{fig:methodology-tradeoff}.  ``Baseline" is the performance of
unmodified ParSplice  measured in trajectory duration (\(y\) axis) and
utilization is measured with memory footprint of just the cache (\(y2\) axis).
The other graph shares the \(y\) axis and shows the trade-off of using a basic
LRU-style cache for different cache sizes, implemented using the ``when" and
``how much" policies in Figure~\ref{src:lru}.  The error bars are the standard
deviation of 3 runs.

\begin{figure}[t]
\footnotesize
\centering
\begin{minted}[xleftmargin=3em,linenos]{lua}
function when()
  if server[whoami]['cachesize'] > n then
    return true
  end
  return false
end

function howmuch()
  if servers[whoami]['cachesize'] > n
    return servers[whoami]['cachesize'] - n
  end
  return 0
end
\end{minted}
\caption{Policy that implements a basic LRU cache. The performance and memory
utilization for different values of \(n\) are graphed in
Figure~\ref{fig:methodology-tradeoff}.
\label{src:lru}}
\end{figure}

@@

The actual policy is shown in Figure~\ref{src:lru-dyn} where the only
difference between the code snippet in Figure~\ref{src:lru} is the addition of
lines 2-9. Note that policy also uses the \texttt{RDState} and \texttt{WRState}
functions described in Section~\S\ref{sec:extracting}.

\begin{figure}[t]
\footnotesize
\centering
\begin{minted}[xleftmargin=3em,linenos]{lua}
function when()
  policy = RDState()
  if policy == 0
    if servers[whoami]['cachesize'] > 100K then
      WRState(1)
      policy = 1
    end
  end
  if policy == 1
    if servers[whoami]['cachesize'] > n then
      return true
    end
  end
  return false
end
\end{minted}
\caption{A more complicated LRU-based cache policy that has two parts. After
absorbing the initial burstiness of the workload, the policy switches to a more
constrained cache to limit memory usage. The performance/utilization for
different values of \texttt{n} is shown in
Figure~\ref{fig:methodology-tradeoff-dynamic}. \label{src:lru-dyn}}
\end{figure}

### 2017-11-10 paper/sections/5_file-systems.tex
paper: addresses #11
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb]
\footnotesize
\begin{minted}[linenos]{lua}
local function when()
  if servers[whoami]["load"] > target then
    if servers[whoami]["load"] > absorb_target then
      WRstate(1)
    end
    if RDstate() == 1 then
      return true
    end
  end
  return false
end
\end{minted}
\caption{ParSplice cache management policy.\label{lua:parsplice}}
\end{figure}

\begin{figure}[tb]
\footnotesize
\begin{minted}[linenos]{lua}
local function when()
  if servers[whoami]["load"] > target then
    overloaded = RDstate() + 1
    WRstate(overloaded)
    if overloaded > 2 then
      return true
    end
  end
  else then
    WRstate(0)
  end
  return false
end
\end{minted}
\caption{CephFS file system metadata load balancer.\label{lua:cephfs}}
\end{figure}

>>>>

\begin{figure}[t]
\footnotesize
\begin{minted}[xleftmargin=3em,linenos]{lua}
local function when()
  if servers[whoami]["load"] > target then
    if servers[whoami]["load"] > absorb_target then
      WRstate(1)
    end
    if RDstate() == 1 then
      return true
    end
  end
  return false
end
\end{minted}
\caption{ParSplice cache management policy.\label{lua:parsplice}}
\end{figure}

\begin{figure}[t]
\footnotesize
\begin{minted}[xleftmargin=3em,linenos]{lua}
local function when()
  if servers[whoami]["load"] > target then
    overloaded = RDstate() + 1
    WRstate(overloaded)
    if overloaded > 2 then
      return true
    end
  end
  else then
    WRstate(0)
  end
  return false
end
\end{minted}
\caption{CephFS file system metadata load balancer.\label{lua:cephfs}}
\end{figure}
